---
title: "Abitibiwinni First Nation and Ouje-Bougoumou Cree Nation Hunting Ground State Assessment"
author: "Annie Claude Bélisle, Hugo Asselin"
date: "August 2020"
output:
  html_document: default
  pdf_document: default
classoption: landscape
---

```{r setup, include=FALSE }
knitr::opts_chunk$set(echo=FALSE,message=FALSE)
```


```{r, include = FALSE} 

# Load the librairies you will need. If they are not installed yet, you will have to do that first: Tools-Install packages

library(ggplot2)
library(gridExtra)
library(rgdal)
library(cowplot)
library(sf)
library(dplyr)
library(cluster)
library(vegan)
library(tidyverse)

# Upload the data sheet.I use a .csv format with ; as separator and , for decimals.  
f <- file.choose()

data <-read.csv(f,sep=";",dec=".",header=TRUE,row.names="hg")

```


```{r, include = FALSE} 

# We need to decide how many clusters we will be using. Write down the minimum an maximum number of groups. 
min_gr<-2
max_gr<-8
# We will run series of k-means on scaled data (mean=0 and square deviation =1)and use SSI and Calinski indicators to find the optimal number of groups. . 

cascade_cal<-cascadeKM(scale(data),inf.gr=min_gr,sup.gr=max_gr,iter=100,criterion="calinski")
cascade_ssi<-cascadeKM(scale(data),inf.gr=min_gr,sup.gr=max_gr,iter=100,criterion="ssi")

plot(cascade_cal)
plot(cascade_ssi)

```

```{r ,include = FALSE} 

# Run k-means again and specify the number of groups. I chose to work with four based on calinski and ssi indices. 
n_gr<-4
km4<-kmeans(scale(data),centers=n_gr,iter.max=100,nstart=5)
Cluster<-km4$cluster

#We wan to get fixed color codes and cluster ID so  we will change the cluster ID according to preset codes based on known cluster members


new_Clu1=which(Cluster==Cluster[which(row.names(data)=="A29")])
new_Clu2=which(Cluster==Cluster[which(row.names(data)=="O59")])
new_Clu3=which(Cluster==Cluster[which(row.names(data)=="O52")])
new_Clu4=which(Cluster==Cluster[which(row.names(data)=="A11")])

Cluster[new_Clu1]=1
Cluster[new_Clu2]=2
Cluster[new_Clu3]=3
Cluster[new_Clu4]=4




#We create a new dataframe including the scaled indicators and the cluster
data_clu=cbind(data.frame(scale(data),Cluster))%>%
  rownames_to_column()%>%
  rename(hg=rowname)




data_clu=cbind(data.frame(scale(data),Cluster))%>%
  rownames_to_column()%>%
  rename(hg=rowname)


```

```{r, include = FALSE} 
# We need to up load the shapefile containing the landscape boundaries. If the shapefile is not located in the same forlder as the .rmd file, it will be necessary to indicate the full direction. The shapefile needs to be in the desired projection. 

map_hg=st_read("hunting_grounds.shp")%>%
  left_join(data_clu, by="hg")

```



|Factor                  | Indicator                              | Code                   |
|------------------------| -------------------------------------  | -----------------------|
|Age structure           |Mature forests                          | `r names(data_clu)[2]` |    
|                        |Regenerating forests                    | `r names(data_clu)[3]` |
|Composition             |Broad-leaved forests                    | `r names(data_clu)[4]` |
|                        |Coniferous forests                      | `r names(data_clu)[5]` |
|                        |Mixedwood forests                       | `r names(data_clu)[6]` |
|Ground state            |Plantations                             | `r names(data_clu)[12]`|
|                        |Windthrow                               | `r names(data_clu)[11]`|
|Naturalness             |Naturalness                             | `r names(data_clu)[7]` |
|Electricity transmission|High voltage power lines                | `r names(data_clu)[13]`|
|Traffic                 |Road density                            | `r names(data_clu)[8]` |
|                        |Distance to town                        | `r names(data_clu)[10]`|
|                        |Lease density                           | `r names(data_clu)[9]` |
|Transportation          |Main road density                       | `r names(data_clu)[14]`|
|Water temperature       |Windthrow in shorelines                 | `r names(data_clu)[15]`|
|Water quality           |Abandoned mining sites                  | `r names(data_clu)[16]`|


```{r, warning = FALSE,out.height="120%",out.width="120%",fig.height=8} 
# Plot loops
data_plot_clu=tbl_df(data_clu)%>%
  arrange(hg)

  
   for(i in 1:nrow(data_plot_clu))
  {
#Use i=1 to test the loop

     ## Hunting_ground ID
   hg_i=as.character(data_plot_clu$hg[i])
   ## we create a table containing  vector hg_x where the current huntng ground has a value of 1 anf others have a value of 0 
    data_plot_i=data_plot_clu%>%
      mutate(hg_x=ifelse(as.character(hg)==hg_i,1,0))
    
    map_hg_i=map_hg%>%
      mutate(hg_x=ifelse(as.character(hg)==hg_i,1,0))
    
    ## Map
  
    map_layout_i=ggplot(data=map_hg_i)+
      geom_sf(aes(fill=as.factor(Cluster),alpha=as.factor(hg_x)))+
      scale_fill_brewer(type = 'qual', palette = "Set2")+
      scale_colour_brewer(type = 'qual', palette = "Set2")+
      scale_alpha_discrete(range=c(0.3, 1))+
      coord_sf(datum=NA,expand = FALSE)+
      theme_void()+
      scale_y_continuous(expand = c(0, 0))+
      theme(legend.position = "none")
    
  ### A loop in the loop to generate dot plots for each indicator
    ### The graph parameters will need to be adjusted (e.g. bin width, x and y limits)
  list_dot_plots=list()
    for(j in 2:ncol(data_plot_clu))
    {
    
  df_j=cbind(data_plot_i[,j],data_plot_i[,"Cluster"],data_plot_i[,"hg_x"])
  df_j$Cluster=as.factor(df_j$Cluster)
  df_j$hg_x=as.factor(df_j$hg_x)
  
  names(df_j)[1]="x"
  
    title_j=as.character(names(data_plot_i)[j])
      
    plot_j=ggplot(df_j,aes(x=x,fill=as.factor(Cluster),colour=as.factor(Cluster),alpha=hg_x))+
      geom_dotplot(binpositions="all",binwidth=0.5,stackgroups = TRUE,method="histodot")+
        theme_classic()+
      labs(y="",x=title_j)+
      scale_fill_brewer(type = 'qual', palette = "Set2")+
        scale_colour_brewer(type = 'qual', palette = "Set2")+
      scale_alpha_discrete(range=c(0.3, 1))+
      ggtitle("") +
      theme(axis.text.x= element_blank(),
            axis.text.y= element_blank(),
            axis.title.x=element_text(title_j),
            axis.line.y = element_blank(),
            axis.ticks.y=element_blank(),
            legend.position="none",
            axis.text=element_text(size=12))+
        #title(main=title_j)+
    scale_x_continuous(expand = c(0.04, 0),limits = c(-4.5,4.5)) + 
    scale_y_continuous(expand = c(0, 0),limits=c(0,30))
      
    
    list_dot_plots[[j-1]]=plot_j
    
  }
      
    ### hunting ground ID
    id=ggdraw() + 
      draw_text(data_plot_i$hg[i], size = 30,fontface = "plain") 
    
   ### we organize the layout in 4 lines
    
    plots=plot_grid(list_dot_plots[[1]],
                    list_dot_plots[[2]],
                    list_dot_plots[[3]],
                    list_dot_plots[[4]],
                    list_dot_plots[[5]],
                    list_dot_plots[[6]],
                    list_dot_plots[[7]],
                    list_dot_plots[[8]],
                    list_dot_plots[[9]],
                    list_dot_plots[[10]],
                    list_dot_plots[[11]],
                    list_dot_plots[[12]],
                    list_dot_plots[[13]],
                    list_dot_plots[[14]],
                    list_dot_plots[[15]],
                    ncol=5)
    
   top=plot_grid(id,map_layout_i,NULL,ncol=3,rel_heights = c(2,7,1))
    
        all=plot_grid(top,plots,nrow=2,rel_heights = c(2,6))
    wow=plot_grid(all,NULL,nrow=2,rel_heights=c(7,1))
    print(wow)
    
    
   #To export in pdf
   # filename_i=paste("C://R//hg_assessment_",data_plot_i$hg[i],".pdf",sep="")
    #ggsave(filename=filename_i,plot=wow,width=8, height = 7,units="in")
    
   } 

```

